The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, ...

### 2012-01-09 bmc_article.tex
Removed lots of comment lines
Added a basic README

%% BioMed_Central_Tex_Template_v1.05
%%                                      %
%  bmc_article.tex            ver: 1.05 %
%                                       %

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                     %%
%%  LaTeX template for BioMed Central  %%
%%     journal article submissions     %%
%%                                     %%
%%         <27 January 2006>           %%
%%                                     %%
%%                                     %%
%% Uses:                               %%
%% cite.sty, url.sty, bmc_article.cls  %%
%% ifthen.sty. multicol.sty		       %%
%%									   %%
%%                                     %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                 %%	
%% For instructions on how to fill out this Tex template           %%
%% document please refer to Readme.pdf and the instructions for    %%
%% authors page on the biomed central website                      %%
%% http://www.biomedcentral.com/info/authors/                      %%
%%                                                                 %%
%% Please do not use \input{...} to include other tex files.       %%
%% Submit your LaTeX manuscript as one .tex document.              %%
%%                                                                 %%
%% All additional figures and files should be attached             %%
%% separately and not embedded in the \TeX\ document itself.       %%
%%                                                                 %%
%% BioMed Central currently use the MikTex distribution of         %%
%% TeX for Windows) of TeX and LaTeX.  This is available from      %%
%% http://www.miktex.org                                           %%
%%                                                                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                              %%
%% You may change the following style settings  %%
%% Should you wish to format your article       %%
%% in a publication style for printing out and  %%
%% sharing with colleagues, but ensure that     %%
%% before submitting to BMC that the style is   %%
%% returned to the Review style setting.        %%
%%                                              %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Begin ...
\begin{document}
\begin{bmcformat}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Enter the title of your article here     %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Enter the authors here                   %%
%%                                          %%
%% Ensure \and is entered between all but   %%
%% the last two authors. This will be       %%
%% replaced by a comma in the final article %%
%%                                          %%
%% Ensure there are no trailing spaces at   %% 
%% the ends of the lines                    %%     	
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Enter the authors' addresses here        %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% The Abstract begins here                 %%
%%                                          %%
%% The Section headings here are those for  %%
%% a Research article submitted to a        %%
%% BMC-Series journal.                      %%  
%%                                          %%
%% If your article is not of this type,     %%
%% then refer to the Instructions for       %%
%% authors on http://www.biomedcentral.com  %%
%% and change the section headings          %%
%% accordingly.                             %%   
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
% Do not use inserted blank lines (ie \\) until main body of text.
\paragraph*{Background:}
Cheminformatics is a well-established field with many applications in chemistry,
drug discovery, and the life sciences. Particularly in the latter field, however,
molecular properties are not well-understood yet, and the interaction between
molecules and larger systems remains a challenge to be modeled. Therefore, the
development of new data mining and pattern recognition continues to be important
and the need for access to a cheminformatics library that one can change remains.

\paragraph*{Results:}
We here report the 1.4 series of the Chemistry Development Kit and outline how
it evolved since the previous report. We demonstrate the new APIs we introduced
in this version and discuss the extensive quality control mechanism we have
adopted. New APIs have been introduced for substructure searching, rendering of
molecules, handling of molecular formulas, atom type perception, and InChI
support. At a quality control side we have introduced automated building,
extensive unit and use case testing, and adopted peer review.

\paragraph*{Conclusions:}
With this paper we have shown the continued effort to provide a free, Open Source
cheminformatics library, and show that such colleborative projects can survive for
a long period. We have taken advantage from the community support, and show
that an open source cheminformatics project can act as a peer reviewed
publishing platform for scientific computating software.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% The Main Body begins here                %%
%%                                          %%
%% The Section headings here are those for  %%
%% a Research article submitted to a        %%
%% BMC-Series journal.                      %%  
%%                                          %%
%% If your article is not of this type,     %%
%% then refer to the instructions for       %%
%% authors on:                              %%
%% http://www.biomedcentral.com/info/authors%%
%% and change the section headings          %%
%% accordingly.                             %% 
%%                                          %%
%% See the Results and Discussion section   %%
%% for details on how to create sub-sections%%
%%                                          %%
%% use \cite{...} to cite references        %%
%%  \cite{koon} and                         %%
%%  \cite{oreg,khar,zvai,xjon,schn,pond}    %%
%%  \nocite{smith,marg,hunn,advi,koha,mouse}%%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection*{New Functionality}

@@

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                  The Bibliography                       %%
%%                                                         %%              
%%  Bmc_article.bst  will be used to                       %%
%%  create a .BBL file for submission, which includes      %%
%%  XML structured for BMC.                                %%
%%                                                         %%
%%                                                         %%
%%  Note that the displayed Bibliography will not          %% 
%%  necessarily be rendered by Latex exactly as specified  %%
%%  in the online Instructions for Authors.                %% 
%%                                                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                               %%
%% Figures                       %%
%%                               %%
%% NB: this is for captions and  %%
%% Titles. All graphics must be  %%
%% submitted separately and NOT  %%
%% included in the Tex document  %%
%%                               %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%
%% Do not use \listoffigures as most will included as separate files

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                               %%
%% Tables                        %%
%%                               %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                               %%
%% Additional Files              %%
%%                               %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%% RESEARCH PAPER %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\begin{bmcformat}

@@

@@

@@

%% The Abstract begins here

\begin{abstract}
% Do not use inserted blank lines (ie \\) until main body of text.
\paragraph*{Background:}
Cheminformatics is a well-established field with many applications in chemistry,
drug discovery, and the life sciences. Particularly in the latter field, however,
molecular properties are not well-understood yet, and the interaction between
molecules and larger systems remains a challenge to be modeled. Therefore, the
development of new data mining and pattern recognition continues to be important
and the need for access to a cheminformatics library that one can change remains.
\paragraph*{Results:}
We here report the 1.4 series of the Chemistry Development Kit and outline how
it evolved since the previous report. We demonstrate the new APIs we introduced
in this version and discuss the extensive quality control mechanism we have
adopted. New APIs have been introduced for substructure searching, rendering of
molecules, handling of molecular formulas, atom type perception, and InChI
support. At a quality control side we have introduced automated building,
extensive unit and use case testing, and adopted peer review.
\paragraph*{Conclusions:}
With this paper we have shown the continued effort to provide a free, Open Source
cheminformatics library, and show that such colleborative projects can survive for
a long period. We have taken advantage from the community support, and show
that an open source cheminformatics project can act as a peer reviewed
publishing platform for scientific computating software.
\end{abstract}

@@

@@

\subsection*{New APIs}

@@

The chemical formula is the basic/simple chemical representation of a compound. It defines the number of atoms/isotopes and type of elements that constitute a chemical compound without describing how atoms are bonded.
It is also the first step toward the identification of the chemical structure from a unidentified compound.

CDK can handle several concepts related to chemical formulas
\begin{itemize}
\item Chemical formula =
\item Set of chemical formulas =
\item Range of chemical formulas =
\item Adducts =
\item Isotope Container =
\item Isotopic pattern = 
\item Rules = Filters in accepting an chemical formula
\end{itemize}

CDK can
\begin{itemize}
\item generate/print the elemental composition from a given IAtomContainer
\item calculate the isotopic pattern from a given chemical formula
\item determine the elemental composition from a given mass
\item validate a chemical formula
\item calculate the exact mass from a given chemical formula
\end{itemize}

Where can it be applied?

@@

Partial atomic charges is an electronic property of atoms defining the asymmetric distribution of electrons in chemical bonds.
It is used as a quantitative correlation with certain compound's physical and chemical properties.

CDK can
\begin{itemize}
\item generate all resonance structures from a given compound 
\item calculate the topological and electronic weight value of each of the resonance structures
\item calculate the partial atomic charge from a given structure 
\end{itemize}

Where can it be applied?

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Figures                       %%

%% Do not use \listoffigures as most will included as separate files

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Tables                        %%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Additional Files              %%
